A portable, annotation-based, visual stepper for Common Lisp

### 2020-04-05 paper/paper.tex
Rework discussion after comments from first reviewer

Its current limitations notwithstanding, the SLY/Emacs stepper
described in this essay is the most effective example of a portable,
visual stepping facility for the Common Lisp ecosystem.  In
formulating its development we have also described (1) a simple,
portable technique for constructing a source-tracking reader in terms
of a compliant reader implementation and (2) a reliable technique to
carry over source-tracking information to macroexpansion.  It is
conceivable that other debugging tools could be constructed from
either of these elements.

>>>>

In formulating the development of the SLY/Emacs stepper, we have also
described (1) a simple, portable technique for constructing a
source-tracking reader in terms of a compliant reader implementation
and (2) a reliable technique to carry over source-tracking information
to macroexpansion.  It is conceivable that other debugging tools could
be constructed from either of these elements.

Its current limitations notwithstanding, the SLY/Emacs stepper
described in this essay is an effective example of a portable, visual
stepping facility for the Common Lisp ecosystem.  To the best of our
knowledge, it is indeed the \emph{only} system that combines these
characteristics.  As such, there is little to compare it against,
except maybe for the aforementioned \texttt{edebug.el}\cite{edebug}
program for the Emacs Lisp language, an annotation-based stepper that
handles macros via user-supplied syntax declarations.  We believe that
the underpinnings of the SLY/Emacs stepper -- \emph{stickers} and
mnesic macroexpansion -- are solid.  We envision enhancements to its
user interface, certainly by incorporating ideas from the interfaces
of non-portable visual Common Lisp steppers, or steppers for other
programming languages.
